%@+leo-ver=4-thin
%@+node:hasletpara.20131202100421.2134:@shadow ./fmpp/Tex/Thesis/Chapters/testing.tex
%@@color
%@@language latex

\chapter{Testing}
In order to test this we must first replicate the work of Apel and Le{\ss}nich

\section{Setting up the enviornment}
The work of Apel and Les{\ss}nich has mostly been done in Java.  There are a few exceptions including the liniar programming libraries that need to be created.  As We are attempting to combine some of their work with Git it was decided to use JGit rather than the C implementation of Git. As the java implimentation may run a bit slower then in order to get a good timing test running we need to run redo the tests of Jdime using Jgit instead. 

Also the tests that Le{\ss}nich did on Jdime were from files rather than from a repository. It is necessary to set the files back up in the original repository structure to get a adequate baseline.

The tests I have written are based on simple changes and the range of refactoings available in the eclispe IDE.  They include such things as changing variable and method names 

Test name, expected optimal result, actual result
Changing comments, no change in target
Changing local variable names, no change in target, the method should be examined to ensure that all variables of that name are changed
Changing private variable names, no change in target,  the class should be examined to ensure that all variables of that name are also changed
Changing default variable names, no change in target, the  package should be examined to ensure all variables with this name are also changed. There is still a risk. A file that is in the same package that has not been placed in the appropriate source dirctory before the merge could no longer compile
%@+at
% insert example
%@-at
%@@c
 
Changing protected variable names, target needs to conflict, The interface between this class and the inheriting class has changed.  The inheriting class could be from a different system.  A change in the variable name could mean that an external program does not compile or run.

Changing public variable names, target needs to conflict, The contract is also changing
Changing private method names, no change in target
Changing default method names, no change in target if the whole package is taken into account
Changing protected variable names, target needs to change as the inherited contract changes
Changing public variable names, target needs to change as contract is also changing 
%@-node:hasletpara.20131202100421.2134:@shadow ./fmpp/Tex/Thesis/Chapters/testing.tex
%@-leo
