
\documentclass[12pt, a4paper, twoside, openright]{book}

\usepackage{vuwthesis} % sets up some local things, mostly the front page

\usepackage{palatino} % sets palatino as the default font

\usepackage{url} % for typesetting urls

\usepackage{graphicx}

\usepackage{listings}

\usepackage{float}

\floatstyle{boxed}
\restylefloat{figure}

%[section] (\usepackage[section]{placeins})

\usepackage[]{algorithm2e}

%\renewcommand{\baselinestretch}{1.00}


\begin{document}

\lstset{language=Java}

\frontmatter
% Book style knows about front matter
% Report style doesn't so you need to set roman numbering etc yourself :-(

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Maintaining differently refactored views in Java}
\author{Paran Haslett}

\subject{Computer Science}
\abstract{
When developers collaborate on a project there are times when the code diverges. This could be due to refactoring or the code being reused in another project. It could even be due to throw away code or code used for debugging. This could at times also involve how the structure of the program is presented or the variable and method names that are being used.  In these cases you may need to refactor the code to best suit your changes before you apply them. The ability to have a separate view which although functionally equivalent to other views can present the code in a different form in these situations would be valuable. It enables the programmer to refactor or change the code with minimal impact on others. Changes in the order of of methods and the addition of comments currently impact other developers even if they do not change how the code works. A tool has been written to detect where source code has been moved within a file or comments has been added removed or edited. This gives us an indication that it would be useful to change version control systems to be aware about items that do not change the functionality of the source code.
}
% Books don't normally have abstracts, and this is a bit of a hack

% Uncomment the appropriate degree
%\phd
\mscthesisonly
%\mscwithhonours
%\mscbothparts
% \otherdegree{DEGREE OR DIPLOMA NAME}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




\maketitle

\include{thesis-acknowledge}

\tableofcontents


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% book style knows about mainmatter
% if you are using report style you will have to rest page numbering etc.
\mainmatter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% individual chapters included here

\include{Chapters/thesis-introduction}
\include{Chapters/Background}
\include{Chapters/Motivation}
\include{Chapters/theTool}
\include{Chapters/expirimentalResults}
\include{Chapters/futureWork}
\include{Chapters/thesis-conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% and of course book style knows about backmatter
% \backmatter caused problems with appendices :-(
% and of course report style doesn't
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\bibliographystyle{ieeetr}
\bibliographystyle{acm}
\bibliography{Thesis}


\end{document}
